---
title: "Comparison Plots"
author: "Indigo Edwards"
date: "9/29/2021"
output: html_document
---

**Please make sure R Markdown in your global settings is set to evaluate code chunks in the PROJECT directory.**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('scripts/data_comparison.R')
```

## NC Botanical Garden 2021

**Reliability 3**

Highest R^2^ values: 

0.0808 for number of frass and caterpillar biomass

0.0398 for mass of frass and caterpillar biomass

```{r NCBG 2021 rel3, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r3,
          Site = 'NC Botanical Garden',
          Year = 2021,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```

**Reliability 2**

Highest R^2^ values:

0.0728 for number of frass and caterpillar biomass

0.0353 for mass of frass and caterpillar biomass

```{r NCBG 2021 rel2, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r2,
          Site = 'NC Botanical Garden',
          Year = 2021,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```

## Prairie Ridge Ecostation 2021

**Reliability 3**

Highest R^2^ values:

0.3092 for frass mass and caterpillar biomass

0.1677 for frass number and caterpillar biomass

```{r PR 2021 rel3, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r3,
          Site = 'Prairie Ridge Ecostation',
          Year = 2021,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```

## NC Botanical Garden 2018

**Reliability 3**

*Data from 2018 have dramatically higher R^2^ values than data from 2021.*

Highest R^2^ values:

0.6101 for frass mass and caterpillar biomass

0.6345 for frass number and caterpillar biomass

```{r NCBG 2018 rel3, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r3,
          Site = 'NC Botanical Garden',
          Year = 2018,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```

## Prairie Ridge Ecostation 2018

**Reliability 3**

Highest R^2^ values:

0.8555 for frass number and caterpillar density

0.8679 for frass number and caterpillar biomass

```{r PR 2018 rel3, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r3,
          Site = 'Prairie Ridge Ecostation',
          Year = 2018,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```