---
title: "More Comparisons"
author: "Indigo Edwards"
date: "10/11/2021"
output: html_document
---

Next steps: 

1. assess lag (-3 to +3 weeks) - make function to shift jweek with lag to compare to cc - R^2 on y as function of lag - same plot can have all three cc vars
1. review papers from UK and Netherlands for comparisons between frass and caterpillar surveys
1. (later) compare between-season phenology - frass/cc centroid difference from overall mean relationship across years
1. (later) write up summary report

```{r setup, include=FALSE}
def <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
  x <- def(x, options)
  ifelse(!is.null(options$suppress), gsub(pattern = "```.*```", "", x), x)
})

knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(fig.width = 12, fig.height = 12)
source('scripts/functions.R')
library(ggplot2)
library(ggpubr)

comp_data <- 
  read_csv(
    'data/processed_data/weekly_stats_2015-2021_rel2.csv')
```

## Frass mass plots

```{r frass mass plots, message = FALSE,echo = FALSE, warning = FALSE, suppress = TRUE}
map(
  c(2015:2019, 2021),
  function(r){
    map(
      c('NC Botanical Garden', 'Prairie Ridge Ecostation'),
      function(s){
        weekly <- 
          comp_data %>% 
          filter(
            year == r,
            site == s) %>% 
          mutate(
            across(c(meanDensity:meanBiomass, mean_mass:mean_number),
                   ~./max(., na.rm = T))) %>% 
          pivot_longer(
            cols = c(meanDensity:meanBiomass, mean_mass),
            names_to = 'variable',
            values_to = 'value') %>% 
          drop_na(value) %>% 
          mutate(variable = factor(
            variable,
            levels = c('mean_mass', 'meanBiomass', 'meanDensity', 'fracSurveys'),
            labels = c('Mean Frass Mass (mg)', 'Mean Caterpillar Biomass (mg)', 'Mean Caterpillar Density', 'Fraction Surveys w/ Caterpillars'))) %>%
          ggplot(
            aes(
              x = julianweek,
              y = value,
              color = variable,
              size = variable)) +
          geom_line() +
          scale_color_manual(
            values = c('black', '#9D10EC', '#334EFF', '#DA0A10')) +
          scale_size_manual(
            values = c(1.5, 0.5, 0.5, 0.5)) +
          labs(
            x = 'Julian Week',
            y = 'Proportion of Maximum')
        
        comps <-
          comp_data %>%
          filter(
            year == r,
            site == s) %>%
          pivot_longer(
            cols = c(meanDensity:meanBiomass),
            names_to = 'variable',
            values_to = 'value') %>%
          mutate(
            variable = factor(
              variable,
              levels = c('meanBiomass', 'meanDensity', 'fracSurveys'),
              labels = c('Mean Caterpillar Biomass (mg)', 'Mean Caterpillar Density', 'Fraction Surveys w/ Caterpillars'))) %>%
          group_by(variable) %>%
          mutate(
            R2 =
              tryCatch(
                summary(lm(value ~ mean_mass))$r.squared %>% round(4),
                        error = function(c){return(0)}),
                height = 0.8*max(value, na.rm = T)) %>%
              ggplot(
                aes(
                  x = mean_mass,
                  y = value,
                  color = variable)) +
              geom_point() +
              geom_smooth(method = 'lm', na.rm = T, se = F) +
              scale_color_manual(
                values = c('#9D10EC', '#334EFF', '#DA0A10')) +
              facet_wrap(~variable, scales = 'free') +
              geom_text(
                aes(
                  x = 0.5*(max(mean_mass, na.rm = T)-min(mean_mass, na.rm = T)),
                  y = height,
                  label = str_c('R^2 = ', R2, sep = ''))) +
              theme(legend.position = 'none') +
              labs(
                x = 'Mean Mass of Frass (mg)',
                y = 'Weekly Mean')
            
            tryCatch(
              ggarrange(
                weekly, comps,
                nrow = 2) %>%
                annotate_figure(
                  top = text_grob(
                    str_c(
                      'CC Variables vs Mean Mass of Frass for',
                      s,
                      'in',
                      r,
                      sep = ' '),
                    face = 'bold',
                    size = 20)),
              error = function(c){})
      })
  })
```

## Frass number plots

```{r frass number plots, message = FALSE, echo = FALSE, warning = FALSE, suppress = TRUE}
map(
  c(2015:2019, 2021),
  function(r){
    map(
      c('NC Botanical Garden', 'Prairie Ridge Ecostation'),
      function(s){
        weekly <- 
          comp_data %>% 
          filter(
            year == r,
            site == s) %>% 
          mutate(
            across(c(meanDensity:meanBiomass, mean_mass:mean_number),
                   ~./max(., na.rm = T))) %>% 
          pivot_longer(
            cols = c(meanDensity:meanBiomass, mean_number),
            names_to = 'variable',
            values_to = 'value') %>% 
          drop_na(value) %>% 
          mutate(variable = factor(
            variable,
            levels = c('mean_number', 'meanBiomass', 'meanDensity', 'fracSurveys'),
            labels = c('Mean Frass Number', 'Mean Caterpillar Biomass (?)', 'Mean Caterpillar Density', 'Fraction Surveys w/ Caterpillars'))) %>%
          ggplot(
            aes(
              x = julianweek,
              y = value,
              color = variable,
              size = variable)) +
          geom_line() +
          scale_color_manual(
            values = c('black', '#9D10EC', '#334EFF', '#DA0A10')) +
          scale_size_manual(
            values = c(1.5, 0.5, 0.5, 0.5)) +
          labs(
            x = 'Julian Week',
            y = 'Proportion of Maximum')
        
        comps <-
          comp_data %>%
          filter(
            year == r,
            site == s) %>%
          pivot_longer(
            cols = c(meanDensity:meanBiomass),
            names_to = 'variable',
            values_to = 'value') %>%
          mutate(
            variable = factor(
              variable,
              levels = c('meanBiomass', 'meanDensity', 'fracSurveys'),
              labels = c('Mean Caterpillar Biomass (?)', 'Mean Caterpillar Density', 'Fraction Surveys w/ Caterpillars'))) %>%
          group_by(variable) %>%
          mutate(
            R2 =
              tryCatch(
                summary(lm(value ~ mean_number))$r.squared %>% round(4),
                        error = function(c){return(0)}),
                height = 0.8*max(value, na.rm = T)) %>%
              ggplot(
                aes(
                  x = mean_number,
                  y = value,
                  color = variable)) +
              geom_point() +
              geom_smooth(method = 'lm', na.rm = T, se = F) +
              scale_color_manual(
                values = c('#9D10EC', '#334EFF', '#DA0A10')) +
              facet_wrap(~variable, scales = 'free') +
              geom_text(
                aes(
                  x = 0.5*(max(mean_number, na.rm = T)-min(mean_number, na.rm = T)),
                  y = height,
                  label = str_c('R^2 = ', R2, sep = ''))) +
              theme(legend.position = 'none') +
              labs(
                x = 'Mean Number of Frass',
                y = 'Weekly Mean')
            
            tryCatch(
              ggarrange(
                weekly, comps,
                nrow = 2) %>%
                annotate_figure(
                  top = text_grob(
                    str_c(
                      'CC Variables vs Mean Number of Frass for',
                      s,
                      'in',
                      r,
                      sep = ' '),
                    face = 'bold',
                    size = 20)),
              error = function(c){})
      })
  })
```


```{r NCBG 2021 single plot, warning = FALSE, include = FALSE}
# weekly <- 
#   comp_data %>% 
#   filter(
#     year == 2021,
#     site == 'NC Botanical Garden') %>% 
#   mutate(
#     across(c(meanDensity:meanBiomass, mean_mass:mean_number),
#            ~./max(., na.rm = T))) %>% 
#   pivot_longer(
#     cols = c(meanDensity:meanBiomass, 'mean_mass'),
#     names_to = 'variable',
#     values_to = 'value') %>% 
#   mutate(variable = factor(
#     variable,
#     levels = c('mean_mass', 'meanBiomass', 'meanDensity', 'fracSurveys'),
#     labels = c('Mean Frass Mass (mg)', 'Mean Caterpillar Biomass (?)', 'Mean Caterpillar Density', 'Fraction Surveys w/ Caterpillars'))) %>%
#   ggplot(
#     aes(
#       x = julianweek,
#       y = value,
#       color = variable,
#       size = variable)) +
#   geom_line() +
#   scale_color_manual(
#     'Variable',
#     values = c('black', '#9D10EC', '#334EFF', '#DA0A10')) +
#   scale_size_manual(
#     values = c(1.5, 0.5, 0.5, 0.5)) +
#   labs(
#     x = 'Julian Week',
#     y = 'Proportion of Maximum')
# 
# comps <- 
#   comp_data %>% 
#   filter(
#     year == 2021,
#     site == 'NC Botanical Garden') %>%
#   pivot_longer(
#     cols = c(meanDensity:meanBiomass),
#     names_to = 'variable',
#     values_to = 'value') %>% 
#   mutate(
#     variable = factor(
#       variable,
#       levels = c('meanBiomass', 'meanDensity', 'fracSurveys'),
#       labels = c('Mean Caterpillar Biomass (?)', 'Mean Caterpillar Density', 'Fraction Surveys w/ Caterpillars'))) %>%
#   group_by(variable) %>% 
#   mutate(
#     R2 = summary(lm(value ~ 'mean_mass'))$r.squared %>% 
#       round(4),
#     height = 0.8*max(value)) %>%
#   ggplot(
#     aes_string(
#       x = 'mean_mass',
#       y = 'value',
#       color = 'variable')) +
#   geom_point() +
#   geom_smooth(method = 'lm', na.rm = T, se = F) +
#   scale_color_manual(
#     values = c('#9D10EC', '#334EFF', '#DA0A10')) +
#   facet_wrap(~variable, scales = 'free') +
#   geom_text(
#     aes(
#       x = 2.5,
#       y = height,
#       label = str_c('R^2 = ', R2, sep = ''))) +
#   theme(legend.position = 'none') +
#   labs(
#     x = 'Mean Mass of Frass (mg)',
#     y = 'Weekly Mean')
# 
# ggarrange(
#   weekly, comps,
#   nrow = 2) %>% 
#   annotate_figure(
#     top = text_grob(
#       'CC Variables vs Mean Mass of Frass for NCBG 2021',
#       face = 'bold',
#       size = 20))

```


