---
title: "Comparison Plots"
author: "Indigo Edwards"
date: "9/29/2021"
output: html_document
---

Next steps: 

1. run code to add dates back to 2015 to summary datasets
1. review papers from UK and Netherlands for comparisons between frass and caterpillar surveys
1. look for papers citing Fischbacher et al. 1998
1. create visual comparison plots for comparing reliabilty 2 and 3 frass data - 2 columns of panels - 1 PR, 1 NCBG, each row is a year, each plot has both reliability options by week - include correlation between reliability options
1. generate weighted average julian week for frass - mean for each data point: sum(x_i_ * y_i_)/sum(x_i_)
1. clean up list labeling on R Markdown
1. compile by week plots into single plot for each frass variable, site, and year combination, in a 2x2 panel with all of the correlation plots
1. convert values to value/max(year, site) so they can all be plotted on the same axis with a legend

**Please make sure R Markdown in your global settings is set to evaluate code chunks in the PROJECT directory.**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('scripts/data_comparison.R')
```

## NC Botanical Garden 2021

**Reliability 3**

Highest R^2^ values: 

0.0808 for number of frass and caterpillar biomass

0.0398 for mass of frass and caterpillar biomass

```{r NCBG 2021 rel3, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r3,
          Site = 'NC Botanical Garden',
          Year = 2021,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```

**Reliability 2**

Highest R^2^ values:

0.0728 for number of frass and caterpillar biomass

0.0353 for mass of frass and caterpillar biomass

```{r NCBG 2021 rel2, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r2,
          Site = 'NC Botanical Garden',
          Year = 2021,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```

## Prairie Ridge Ecostation 2021

**Reliability 3**

Highest R^2^ values:

0.3092 for frass mass and caterpillar biomass

0.1677 for frass number and caterpillar biomass

```{r PR 2021 rel3, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r3,
          Site = 'Prairie Ridge Ecostation',
          Year = 2021,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```

## NC Botanical Garden 2018

**Reliability 3**

*Data from 2018 have dramatically higher R^2^ values than data from 2021.*

Highest R^2^ values:

0.6101 for frass mass and caterpillar biomass

0.6345 for frass number and caterpillar biomass

```{r NCBG 2018 rel3, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r3,
          Site = 'NC Botanical Garden',
          Year = 2018,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```

## Prairie Ridge Ecostation 2018

**Reliability 3**

Highest R^2^ values:

0.8555 for frass number and caterpillar density

0.8679 for frass number and caterpillar biomass

```{r PR 2018 rel3, message = FALSE, echo = FALSE, warning = FALSE}
map(
  c('mean_mass', 'mean_number'),
  function(x){
    map(
      c('meanBiomass', 'meanDensity', 'fracSurveys'),
      function(y) {
        comp_plot(
          Data = comp_data_r3,
          Site = 'Prairie Ridge Ecostation',
          Year = 2018,
          frass_var = x,
          cc_var = y)
      }
    )
  }
)
```