---
title: "Comparing Reliability"
author: "Indigo Edwards"
date: "10/1/2021"
output: html_document
---

Next steps: 

1. review papers from UK and Netherlands for comparisons between frass and caterpillar surveys
1. clean up list labeling on R Markdown
1. compile by week plots into single plot for each frass variable, site, and year combination, in a 2x2 panel with all of the correlation plots
1. convert values to value/max(year, site) so they can all be plotted on the same axis with a legend

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(fig.width = 12, fig.height = 12)
source('scripts/functions.R')
library(ggplot2)
library(ggpubr)
comp_data_r1 <- 
  read_csv(
    'data/processed_data/weekly_stats_2015-2021_rel1.csv')
comp_data_r2 <- 
  read_csv(
    'data/processed_data/weekly_stats_2015-2021_rel2.csv')
comp_data_r3 <- 
  read_csv(
    'data/processed_data/weekly_stats_2015-2021_rel3.csv')
```



$$\\[1in]$$

```{r mass plots, message = FALSE, echo = FALSE, warning = FALSE}
mm_list <- 
  map(
    c('NC Botanical Garden', 'Prairie Ridge Ecostation'),
    function(y){
      map(
        c(2015:2019, 2021),
        function(x){
          
          c3 <- 
            comp_data_r3 %>% 
            filter(
              site == y,
              year == x)
          
          c2 <- 
            comp_data_r2 %>% 
            filter(
              site == y,
              year == x)
          
          ggplot(
            data = c3 %>% drop_na(mean_mass),
            mapping = aes(
              x = julianweek,
              y = mean_mass,
              color = factor(reliability))) +
            geom_point() +
            geom_line() +
            geom_vline(
              xintercept = sum(c3$julianweek * c3$mean_mass, na.rm = T) /
                sum(c3$mean_mass, na.rm = T),
              linetype = 'dashed',
              color = 'red') +
            geom_point(data = c2 %>% drop_na(mean_mass)) +
            geom_line(data = c2 %>% drop_na(mean_mass)) +
            geom_vline(
              xintercept = sum(c2$julianweek * c2$mean_mass, na.rm = T) /
                sum(c2$mean_mass, na.rm = T),
              linetype = 'dashed',
              color = 'forestgreen') +
            scale_x_continuous(breaks = c2 %>% pull(julianweek)) +
            labs(
              color = 'Reliability',
              tag = 
                paste(
                  'R^2 = ',
                  tryCatch(
                    summary(lm(c3$mean_mass ~ c2$mean_mass))$r.squared %>% 
                      round(4),
                    error = function(c){return(paste(''))}),
                  sep = '')) +
            theme(
              plot.tag.position = c(0.2,0.8),
              axis.title.x = element_blank(),
              axis.title.y = element_blank()) +
            scale_color_manual(values = c('forestgreen', 'red'))
        })
    })

ncbg_mass_temp <- 
  ggarrange(
    plotlist = mm_list[[1]], 
    ncol = 1,
    labels = c(2015, 2016, 2017, 2018, 2019, 2021),
    hjust = 1.2,
    vjust = 5,
    legend = 'none') +
  theme(plot.margin = margin(0.1, 0.1, 0.1, 2, 'cm'))
  
ncbg_mass_plots <- 
  annotate_figure(
    ncbg_mass_temp,
    top = text_grob(
      'NC Botanical Garden',
      face = 'bold',
      size = 20),
    left = text_grob(
      'Mean Mass of Frass',
      size = 16,
      rot = 90))

pr_mass_temp <- 
  ggarrange(
    plotlist = mm_list[[2]], 
    ncol = 1,
    hjust = 1,
    vjust = 5,
    legend = 'none')

pr_mass_plots <- 
  annotate_figure(
    pr_mass_temp,
    top = text_grob(
      'Prairie Ridge Ecostation',
      face = 'bold',
      size = 20))

ggarrange(
  ncbg_mass_plots,
  pr_mass_plots,
  ncol = 2,
  widths = c(1.1,1),
  legend.grob = get_legend(mm_list[[1]][[1]])) %>% 
  annotate_figure(
    top = text_grob(
      'Comparison by Reliability for Mean Mass of Frass',
      size = 28,
      face = 'bold'),
    bottom = text_grob(
      'Julian Week',
      size = 16))
```

$$\\[1in]$$

```{r number plots, message = FALSE, echo = FALSE, warning = FALSE}
mn_list <- 
  map(
    c('NC Botanical Garden', 'Prairie Ridge Ecostation'),
    function(y){
      map(
        c(2015:2019, 2021),
        function(x){
          
          c3 <- comp_data_r3 %>% 
              filter(
                site == y,
                year == x)
          
          c2 <- comp_data_r2 %>% 
                filter(
                  site == y,
                  year == x)
          
          ggplot(
            data = c3 %>% drop_na(mean_number),
            mapping = aes(
              x = julianweek,
              y = mean_number,
              color = factor(reliability))) +
            geom_point() +
            geom_line() +
            geom_vline(
              xintercept = sum(c3$julianweek * c3$mean_number, na.rm = T) /
                sum(c3$mean_number, na.rm = T),
              linetype = 'dashed',
              color = 'red') +
            geom_point(data = c2 %>% drop_na(mean_number)) +
            geom_line(data = c2 %>% drop_na(mean_number)) +
            geom_vline(
              xintercept = sum(c2$julianweek * c2$mean_mass, na.rm = T) /
                sum(c2$mean_mass, na.rm = T),
              linetype = 'dashed',
              color = 'forestgreen') +
            scale_x_continuous(breaks = c2 %>% pull(julianweek)) +
            labs(
              color = 'Reliability',
              tag = 
                paste(
                  'R^2 = ',
                  tryCatch(
                    summary(lm(c3$mean_number ~ c2$mean_number))$r.squared %>% 
                      round(4),
                    error = function(c){return(paste(''))}),
                  sep = '')) +
            theme(
              plot.tag.position = c(0.2,0.8),
              axis.title.x = element_blank(),
              axis.title.y = element_blank()) +
            scale_color_manual(values = c('forestgreen', 'red'))
        })
    })

ncbg_number_temp <- 
  ggarrange(
    plotlist = mn_list[[1]], 
    ncol = 1,
    labels = c(2015, 2016, 2017, 2018, 2019, 2021),
    hjust = 1.2,
    vjust = 5,
    legend = 'none') +
  theme(plot.margin = margin(0.1, 0.1, 0.1, 2, 'cm'))
  
ncbg_number_plots <- 
  annotate_figure(
    ncbg_number_temp,
    top = text_grob(
      'NC Botanical Garden',
      face = 'bold',
      size = 20),
    left = text_grob(
      'Mean Number of Frass',
      size = 16,
      rot = 90))

pr_number_temp <- 
  ggarrange(
    plotlist = mn_list[[2]], 
    ncol = 1,
    hjust = 1,
    vjust = 5,
    legend = 'none')

pr_number_plots <- 
  annotate_figure(
    pr_number_temp,
    top = text_grob(
      'Prairie Ridge Ecostation',
      face = 'bold',
      size = 20))

ggarrange(
  ncbg_number_plots,
  pr_number_plots,
  ncol = 2,
  widths = c(1.1,1),
  legend.grob = get_legend(mn_list[[1]][[1]])) %>% 
  annotate_figure(
    top = text_grob(
      'Comparison by Reliability for Mean Number of Frass',
      size = 28,
      face = 'bold'),
    bottom = text_grob(
      'Julian Week',
      size = 16))
```



